\chapter{Conclusion}

\noindent A large language model or action model for transaction processing can provide a powerful tool for users to interact with a transaction processing system. The LLM can interpret user queries and generate corresponding outputs in the form of JSON files, which can be used to perform various transaction-related operations. This can help to simplify the transaction process and make it more accessible to users who may not be familiar with the underlying technology.

\noindent The addition of user permissions to the system can help to ensure that sensitive data is protected and that only authorized operations are performed. By requiring users to authenticate themselves and granting them access to specific resources based on their permissions, the system can help to prevent unauthorized access and ensure that data is handled securely.

\noindent Overall, a large language model or action model for transaction processing can provide a seamless and natural way for users to interact with a transaction processing system, while also ensuring that sensitive data is protected and that only authorized operations are performed. This can help to improve the efficiency and effectiveness of transaction processing, while also ensuring that data is handled securely and in compliance with relevant regulations.

\clearpage`
\section{Future Scope}

There are several areas where this system could be further developed and enhanced in the future. Here are a few potential ideas:

\begin{enumerate}

\item \textbf{Improved natural language understanding:}   While the LLM in your system is already quite powerful, there is always room for improvement in natural language understanding. You could explore techniques such as transfer learning or fine-tuning to improve the LLM's ability to interpret complex queries and handle ambiguous language.


\item \textbf{Multi-Modal Input:}   Currently, your system only accepts text-based queries. However, there are many situations where it might be useful to accept other types of input, such as voice commands or even gestures. Exploring multi-modal input methods could make your system more versatile and user-friendly.

\item \textbf{Advanced Access Control:} While your system already includes user permissions, there may be situations where more advanced access control is needed. For example, you might implement role-based access control (RBAC) to allow different users to have different levels of access based on their role within an organization.

\item \textbf{Integration with Other Systems: } Your system could be integrated with other systems to provide even more powerful capabilities. For example, you might integrate with a customer relationship management (CRM) system to enable users to perform transactions related to customer accounts, or with an accounting system to enable users to perform financial transactions.


\item \textbf{Real-Time Analytics:} While your system currently focuses on performing individual transactions, there is potential to add real-time analytics capabilities to provide insights and trends based on transaction data. This could help users make more informed decisions and optimize their transaction processes.



\end{enumerate}
Improved natural language understanding will provide a more user-friendly, accurate, efficient, and secure system for transaction processing, improving the overall user experience and providing greater value to businesses.

\section{Limitations}
large language models have the potential to greatly enhance transaction processing, and ongoing research and development efforts are focused on addressing these challenges and unlocking the full potential of these models.
However, it is important to acknowledge that the project does have certain limitations. The limitations are:

\begin{itemize}
    \item Large language models require vast amounts of data for training, which can raise concerns around data security and privacy. Ensuring that sensitive data is protected and not misused is a critical challenge.

    \item While large language models can generate human-like text, they may struggle with understanding context and nuance, leading to inaccuracies or misunderstandings in transaction processing.
    
    \item Large language models may struggle to interpret ambiguous queries, leading to errors or misunderstandings in transaction processing.

    \item  While large language models can perform a variety of tasks, they may struggle to handle multiple tasks simultaneously, leading to decreased efficiency in transaction processing.
\end{itemize} 